\documentclass{cv_style}

\setname{Taylor}{Martin}
\setaddress{Coeur d' Alene, ID}
\setmobile{208-771-1745}
\setmail{mart8517@vandals.uidaho.edu}
\setlinkedinaccount{https://www.linkedin.com/in/taylor-martin-xv/}
\setgithubaccount{https://github.com/Trmart}
\setthemecolor{violet}

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
\setcompanyname{COMPANY NAME}
\setcontactperson{Hiring Manager}
\setclaimedposition{Junior Software Engineer}
\coverletter{ %

I am excited to apply for the Junior Software Engineer position at your company. With over 5 years of experience in Computer Science and 1 year of full-time programming experience, I am confident in my ability to contribute to your team.


As a graduate of the University of Idaho with a BS in Computer Science and a 3.65 Overall GPA, I have developed a strong foundation in programming principles, data structures, algorithms, and software development methodologies. Additionally, I possess excellent oral and written communication skills, which have allowed me to effectively collaborate with cross-functional teams, present complex technical information to non-technical stakeholders, and write clear and concise documentation.


Throughout my career, I have demonstrated a passion for learning and a dedication to continuous improvement. I am proficient in multiple programming languages including C, C++, C\#, and Python, and have experience working with web technologies such as HTML, CSS, Flask, Laravel, and Bootstrap. I have also worked on projects involving databases, cloud computing, and machine learning.


I am eager to explore opportunities within your company and contribute to its success. Please find my resume attached for your consideration. If you have any questions or would like to schedule an interview, please do not hesitate to contact me. I am available for an interview at your convenience.


Thank you for considering my application. I look forward to the opportunity to discuss my qualifications further.

Sincerely,
Taylor Martin
}
\end{document}
