\documentclass{cv_style}

\setname{Taylor}{Martin}
\setaddress{Coeur d' Alene,ID}
\setmobile{208-771-1745}
\setmail{mart8517@vandals.uidaho.edu}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/taylor-martin-xv/}
\setgithubaccount{https://github.com/Trmart}
\setthemecolor{violet} %you can play with color of the template (red is also nice..)




\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}
{%
Computer science graduate with experience in programming, software development, and project management. Skilled in C++, C, C\#, Python, and web development. Completed a senior capstone engineering project for SEL, automating a manufacturing job. Seeking a software development position with a dynamic company.
}
%
%Education
\section{Education} 
    \datedexperience{North Idaho College}{2018 - 2021} 
    \explanation{A.S in Computer Science} 
     \explanationdetail{\coloredbullet\ %
        3.5 GPA. With Minor in Mathematics.
        Developed a Lexical Analyzer from scratch in C.
        Created a Spotify playlist clone with linked lists in C++.
        Developed system software apps in C, including a shell and recycle bin.
        Implemented an OS scheduler in C using queues, threads, mutex, and semaphores.
        Built games using C\# in Unity.
     }
    \datedexperience{University of Idaho}{2021 - 2023} 
    \explanation{B.S in Computer Science} 
    \explanationdetail{\coloredbullet\ %
3.65 GPA with a minor in Mathematics.
Led and programmed an indie game studio in Unity using C\#, completing the project ahead of schedule.
Developed web applications with Flask, Laravel, and MySQL for both front-end and back-end.
Created a genetic algorithm framework for computational biology simulation in Python.
Built a compiler for an imaginary c- programming language using C, C++, Flex, and Yacc.
Modeled and trained AI using Python's machine learning algorithms and training datasets.
Built a 2D and 3D Graphics Engine in C++.
    }
    \datedexperience{Completed Coursework}{2018 - 2023} 
    \explanation{Computer Science} 
    \explanationdetail{\coloredbullet\ %
    Theory of Programming Languages, Computer Operating Systems, System Software, Database Systems, Computer Graphics, Machine Learning, Analysis of Algorithms and Abstract Data Structures, Theory of Computation, Software Engineering, Computational Biology, Artificial Intelligence, Contemporary Issues in Computer Science, Compiler Design, Senior Capstone Design (2 semesters).
    }
    \explanation{Mathematics}
    \explanationdetail{\coloredbullet\ %
    Calculus I-III, Linear Algebra, Discrete Mathematics, Probability and Statistics for Engineering. 
     }
%
% Experience
\section{Experience}
    % 
       
    \datedexperience{Polymorphic Games Studios | University of Idaho}{2022-2023 / Moscow, ID} 
    \explanation{Full-Time Software Engineer} 
    \explanationdetail{\coloredbullet\ %
    Wrote code for multiple aspects of the Steam game Pakicetus in C\#, contributed to the game's overall vision, utilizing agile methodology and OOP.
    %
    }
    \datedexperience{Pilgrims Natural Market}{2019-2022 / Coeur d' Alene, ID} 
    \explanation{Cashier}
    \explanationdetail{\coloredbullet\ %
    Consistently exceeded sales goals and developed strong communication skills.
    }
    %
    \datedexperience{U.S. Bank}{2015-2019 / Couer d' Alene, ID} 
    \explanation{Universal Banker} 
    \explanationdetail{\coloredbullet\ %
    Promoted to Universal Banker and achieved certification as a Universal Banker. 
     }
    % 
    \explanation{Credit Analyst} 
    \explanationdetail{\coloredbullet\ %
    Streamlined customer service operations and earned certification as a credit specialist and fraud analyst.
     }
    %
    \datedexperience{Wells Fargo}{2013 - 2015 / Couer d' Alene, ID} 
    \explanation{Bank Teller} 
    \explanationdetail{\coloredbullet\ %
     Consistently exceeded sales goals and built strong relationships with customers. Trained new hires on policies and procedures.
     }


% Projects
\section{Projects}
    %
    \datedexperience{Keynetics Key Assembler Automation Project}{2022-2023 / University of Idaho} 
    \explanation{Senior Capstone Engineering Project}
    \explanationdetail{\coloredbullet\ %
    Led a team to design and build the Keynetics Assembler, automating a manufacturing job SEL. Created a user-friendly web application for plug configuration management. Built a custom manufacturing station with robots, UV flood lights, and a plug oven to automate the dispensing and curing of UV resin. Completed the project ahead of schedule and under budget, demonstrating effective project management skills.
     }
    %
    \datedexperience{Pakicetus.}{2022-2023 / Polymorphic Game Studio} 
    \explanation{Underwater Rogue-Like Exploration Game } 
    \explanationdetail{\coloredbullet\ %
    Funded by the NSL. Pakicetus is a deep-sea rogue-lite exploration game. As captain of the Salvation, you must balance resource collection, system upgrades, and a dwindling food supply as you battle against an unknown enemy bent on stopping your search for a new home. 
     }


%
% Skills
\section{Programming Languages \& Technologies}
    %
    \explanationdetail{\coloredbullet\ %
    C++, C, C\#, Python, SQL, PHP, Make, Bash, HTML 5, CSS


    
    \coloredbullet\ %
    VS Code, Git, Plastic, Slack, Discord, Linux, Unity, VIM, VM, Flask, Laravel, Bootstrap 5, PHPmyAdmin Server. 
    }
    %
%
%
%Footnote
\end{document}
